### 2021-11-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@988ab764fd8e5bae8d99ac2200bddea12f7d3be8 🚀

@@

As a result \emph{ecological forecasting}, or building models to
estimate how ecological systems will change over time, has as an
imperative to mitigate the effect of these changes on Earth's
ecosystems, their functioning, and the services they provide to humans
(\textbf{dietze?}).

@@

In recent years, there has been an interest in an epistemological shift
in ecology. To shift ecology into a predictive science. The
justification for this shift is twofold: (1) bogged down philosophy of
science, by further rooting our understanding of ecosystem function and
dynamics in an ability to predict their structure
(\textbf{PredictiveEcology?}). and (2) the practical need for models for
\emph{ecological forecasting}.

@@

\begin{itemize}
\tightlist
\item
  Often assume long-run equilibrium.
\end{itemize}

@@

\hypertarget{methods-2}{%
\section{Methods}\label{methods-2}}

@@

>>>>

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

As a result \emph{ecological forecasting}, or building models to
estimate how ecological systems will change over time, has as an
imperative to mitigate the effect of these changes on Earth's
ecosystems, their functioning, and the services they provide to humans
(Dietze 2017).

@@

In recent years, there has been an interest in an epistemological shift
in ecology. To shift ecology into a predictive science. The
justification for this shift is twofold: (1) bogged down philosophy of
science, by further rooting our understanding of ecosystem function and
dynamics in an ability to predict their structure (Dietze 2017). and (2)
the practical need for models for \emph{ecological forecasting}.

@@

Often assume long-run equilibrium.

@@

\hypertarget{methods-2}{%
\subsection{Methods}\label{methods-2}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Dietze2017PreEco}{}%
Dietze, M.C. (2017). Prediction in ecology: A first-principles
framework. \emph{Ecological Applications}, 27, 2048--2060.

\end{CSLReferences}
